Solving Horn clauses over LI

### 2012-12-20 article.tex

@@

<x> ::= $e$ | $p$

@@

* We consider inequalities.
** NOTE: Even we have =, $\neq$, >, <=, we can normalize to >=
         over integer space

\subsection{Generating a tree}

@@

Def <Implication Tree>:

Implication tree is such a tree that every node is labeled by logical
atoms. The label of every node is implied by the conjunction of its
children's label.

>>>>

The input for our algorithm is a set of Horn clauses. They contain linear inequalities on real numbers and unknown predicate symbols. With having real numbers $n$ and variables $v$, the syntax is defined as follows. Predicate symbols $P$ are represented by capital alphabet through this paper.

@@

<x> ::= $e$ | $p$  % Horn term

@@

Although we limit the input only to linear inequalities with $\leq$, we will later extend to any linear arithmetic expressions by introducing disjunctions in $e$.

\subsection{Generating a implication tree}

@@

---
Def <Implication Tree>:
Implication tree is such a tree that every node is labeled by a Horn term. As the semantics of the tree, the Horn term of every node is implied by the conjunction of its children's Horn terms.
---

In the implication tree, every relationship from a certain node to its children corresponds to one Horn clause of the original input. All leaves and the root node have linear expressions $e$ while all other have predicate symbols $p$. Therefore

We show the pseudo code for generating a tree.

\begin{algorithm}
\caption{$\mbox{\sc BuildTree}$}
\begin{algorithmic}
\item pseudo-code
\end{algorithmic}
\end{algorithm}

While building a tree, renaming should be accordingly to make the construct.
